\begin{titlepage} My paper \end{titlepage}

### 2018-08-23 paper/drafts/draft3.tex
New data

	In this paper, we present a closed loop control system that builds upon the ideas of Mahoney and Bangura while reducing the computational complexity through the use of sensors.

	\section{II}
	%Talk about the theory of the wind.
	%Theory of things like the low pass filter, the algoright, the PID controller, and whatever else we have. Maybe even the statistics
	We have to start by defining the three different velocities that we are measuring.\\
	\begin{eqnarray}
	\label{e1}
	v_x , v_y , v_z \\
	\label{e2}
	v^s_{x} , v^s_{y} , v^s_{z} \\
	\label{e3}
	v^i_{x} , v^i_{y} , v^i_{z}
	\end{eqnarray}
	Where \ref{e1} Is the velocity of the drone, the body frame velocity. \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
	\begin{eqnarray}
	\nonumber
	v_s = v^s_{z}\\
	\nonumber
	v_i = v^i_{z}
	\end{eqnarray}
	What the wind sensor will notice is 
	\begin{equation}
	v_{tot} = v_{i} + v_{s}
	\label{vtot}
	\end{equation}	
	\section{III} 
	%THE THRUST STAND
	In our setup we used a thrust stand obtained from RCBenchmark. This thrust stand incorporates an arduino board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is a GUI which allows us to collect and visualize the data. From measuring the pulse rate of the board, we can see that the board collects data at a 1kHz speed. At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds to external stimuli. The measurement from the thrust stand will be our "ground truth".

>>>>

	In this paper, we present a novel control system for MAV's based around a sensor that measures wind speed and uses a observer kalman filter to handle the data and provide an optimal output to maintain a desired thrust value. The goal of our system is to provide a similar or better response to that of Mahoney et al. while also being computationally less intense. 
	\section{Paper Review}
	Yeo et al. developed a pitot tube method of sensing the wind speed. The purpose of their sensing was for detection of other drones, but their method can be related to. The pitot tubes are connected to a sensor that measures changes in pressure. They detail a relationship between wind speed and pressure and therefore use detected pressure to measure the overall downwash windspeed of each propeller. Their results showed a high level of response to changes in wind with a high level of accuracy. The issue that was faced was that there was a very limited range under which the drone could
	\section{II}
	%Talk about the theory of the wind.
	%Theory of things like the low pass filter, the algoright, the PID controller, and whatever else we have. Maybe even the statistics
	We have to start by defining the three different velocities that we are measuring.\\
	\begin{eqnarray}
	\label{e1}
	v_x , v_y , v_z \\
	\label{e2}
	v^s_{x} , v^s_{y} , v^s_{z} \\
	\label{e3}
	v^i_{x} , v^i_{y} , v^i_{z}
	\end{eqnarray}
	Where \ref{e1} Is the velocity of the drone, the body frame velocity. \ref{e2} is the velocity of the wind approaching the propellers, the stream velocity, and \ref{e3} is the induced velocity of the propellers.\\
	Since we are doing only the static tests, we do not have to worry about horizontal winds, so we can say 
	\begin{eqnarray}
	\nonumber
	v_s = v^s_{z}\\
	\nonumber
	v_i = v^i_{z}
	\end{eqnarray}
	What the wind sensor will notice is 
	\begin{equation}
	v_{tot} = v_{i} + v_{s}
	\label{vtot}
	\end{equation}	
	\section{III} 
	%THE THRUST STAND
	In our setup we used a thrust stand obtained from RCBenchmark. This thrust stand incorporates an arduino board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is a GUI which allows us to collect and visualize the data. From measuring the pulse rate of the board, we can see that the board collects data at a 1kHz speed. At this rate, it is much faster than most ESC's and FC's and therefore is an adequate way to measure how the system responds to external stimuli. The measurement from the thrust stand will be our "ground truth".
